### 2015-02-15 Docs/architecture/architecture.tex

\begin{figure}[]
\centering
\includegraphics[scale=0.55]{\archfigpath/maestro_ecosystem2}
\caption[\maestro\ `ecosystem'] {\label{fig:arch:eco} The basic
  \maestro\ `ecosystem'.  Here we see the different packages that
  contribute to building the {\tt test2} problem in \maestro.  The
  red directories are part of most standard \maestro\ build.  The
  purple lines show the directories that are pulled in through
  various Makefile variables ({\tt BOXLIB\_HOME}, {\tt NETWORK\_DIR},
  {\tt EOS\_DIR}, and {\tt CONDUCTIVITY\_DIR}).}
\end{figure}

@@

The best way to customize the initialization (e.g.\ add perturbations)
is to copy from one of the existing problems.  The file \code{initveldata.f90} controls the velocity field initialization and \code{initscaldata.f90} controls the initialization of the scalars
($\rho$, $\rho X_k$, $\rho h$).  The {\tt test2} problem is a good
starting point for plane-parallel and {\tt wdconvect} is a good
starting point for full stars.

>>>>

\begin{figure}[]
\centering
\includegraphics[scale=0.55]{\archfigpath/maestro_ecosystem2}
\caption[\maestro\ `ecosystem'] {\label{fig:arch:eco} The basic
  \maestro\ `ecosystem'.  Here we see the different packages that
  contribute to building the {\tt reacting\_bubble} problem in \maestro.  The
  red directories are part of most standard \maestro\ build.  The
  purple lines show the directories that are pulled in through
  various Makefile variables ({\tt BOXLIB\_HOME}, {\tt NETWORK\_DIR},
  {\tt EOS\_DIR}, and {\tt CONDUCTIVITY\_DIR}).}
\end{figure}

@@

The best way to customize the initialization (e.g.\ add perturbations)
is to copy from one of the existing problems.  The file \code{initveldata.f90} controls the velocity field initialization and \code{initscaldata.f90} controls the initialization of the scalars
($\rho$, $\rho X_k$, $\rho h$).  The {\tt reacting\_bubble} problem is a good
starting point for plane-parallel and {\tt wdconvect} is a good
starting point for full stars.
